---
title: "Marketing Report"
author: Pei Sin Ang
format:
    html: 
      theme: cosmo
      toc: true
    pdf:
      toc: true
---


```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE) 
```

```{r}
# Libraries required in this report. Install packages as required.
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
```

## Introduction
This report investigates wether higher marketing spend per customer lead to higher purchase amounts using the campaign data of 150 customers. Understanding this relationship will allow us to optimise future marketing budgets towards customers who generate more return.

## Research question
We want to know if higher marketing spend per customer lead to higher purchase amounts by using 'marketing_spend' and 'purchase_amount' from the campaign data. A linear regression model will be used to determine if marketing spend can effectively predict customer purchase amount.

## Dataset Introduction
```{r}
campaign_data <- read.csv("data/35789190_Pei_Ang.csv")

campaign_data_clean <- campaign_data |> 
    mutate(signup_date = na_if(signup_date, "N/A"),
        signup_date = as_date(parse_date_time(signup_date, orders = c("ymd", "dmy", "BdY")))) |> 
    filter(!is.na(purchase_amount)) |> 
    select(-notes)
```

The cleaned dataset records a total of 132 different customers. It keeps a record of the 'signup_date', 'marketing_spend', number of website 'visits', 'purchase_amount', and the customer 'segment' (Consumer, SMB or Enterprise).

During cleaning, 'signup_date' was stored as a character string with inconsistent formats (e.g. '2025-08-22', 'May 17, 2025', '21/12/2024'). It was then converted to a consistent ISO date format. 

The'notes' column was also removed as it was to inconsistently documented and not relevant to the research question. 

Rows with missing 'purchase_amount' were also removed as they are unrecorded data that cannot contribute to the analysis.

### Dataset Description
The cleaned data set contains `r nrow(campaign_data_clean)` observations and `r ncol(campaign_data_clean)` variables.

```{r}
#| label: fig-customers-by-segment
#| fig-cap: "Number of Customers by Segment"
ggplot(campaign_data_clean, aes(x = segment, fill = segment)) + 
    geom_bar() +
    labs(
    x = "Segment",
    y = "No. of Customers") +
    theme_bw()
```


```{r}
#| label: tbl-summmary-statistic
#| tbl-cap: "Min, Max, Mean of Marketing Spend and Purchase Amount"
#| tbl-cap-location: bottom
campaign_data_clean |> 
    summarise(
        min_mkting_spend = min(marketing_spend), 
        max_mkting_spend = max(marketing_spend),
        avg_mkting_spend = mean(marketing_spend),
        min_purchase_amt = min(purchase_amount),
        max_purchase_amt = max(purchase_amount),
        avg_purchase_amt = mean(purchase_amount)
    ) |> 
    knitr::kable(digits = 2)
```

## Results
```{r}
#| label: fig-marketing-spend-vs-purchase-amt
#| fig-cap: "Marketing Spend vs Purchase Amount"
ggplot(campaign_data_clean, aes(x = marketing_spend, y = purchase_amount)) + 
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    labs(
        x = "Marketing Spend ($)",
        y = "Purchase Amount ($)") +
    theme_bw()
```


```{r}
#| label: fig-segmented-marketing-spend-vs-purchase-amt
#| fig-cap: "Marketing Spend vs Purchase Amount by Segment"
ggplot(campaign_data_clean, aes(x = marketing_spend, y = purchase_amount, colour = segment)) + 
    facet_wrap(~segment) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    labs(
        x = "Marketing Spend ($)",
        y = "Purchase Amount ($)") +
    theme_bw() + 
    theme(legend.position = "bottom")
```

```{r}
slopes <- campaign_data_clean |> 
    group_by(segment) |> 
    summarise(slope = coef(lm(purchase_amount ~ marketing_spend))[2])
```

@fig-marketing-spend-vs-purchase-amt shows an overall positive relationship between marketing spend and purchase amount. This suggests that higher marketing spend does lead to higher purchase amounts.

@fig-segmented-marketing-spend-vs-purchase-amt breaks down the relationship between marketing spend and purchase amount by customer segment. All three segments have a positive relationship, with Consumer customers showing the most data point, and the Enterprise showing the fewest. 

The slope of the regression line in @fig-segmented-marketing-spend-vs-purchase-amt for Consumer customers is `r round(slopes$slope[1], 2)`, Enterprise customers is `r round(slopes$slope[2], 2)`, and SMB customers is `r round(slopes$slope[3], 2)`. This means that for every $1 increase in marketing spend, the purchase amount increases by $`r round(slopes$slope[1], 2)`, $`r round(slopes$slope[2], 2)` and $`r round(slopes$slope[3], 2)` for Consumer, Enterprise and SMB customers respectively. 

This result suggests that the Enterprise customers with the gentlest slope is less effective at driving purchase amounts with higher marketing spend than SMB customers with the steepest slope.

Overall, the results do suggest that higher marketing spend does lead to higher purchase amounts across all segments, with SMB customers generating the highest return per dollar of marketing spend. It is also good to note that Consumer customers are not too far away from SMB customers in generating a high return per dollar of marketing spend. Future marketing budget can prioritise SMB and Consumers for an optimised return.