---
title: "Marketing Report"
format:
    html: 
        theme: cosmo
    pdf:
        toc: false
---


```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE) 
```

```{r}
# Libraries required in this report. Install packages as required.
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
```

### Introduction
This report investigates wether higher marketing spend per customer lead to higher purchase amounts using the campaign data of 150 customers. Understanding this relationship will allow us to optimise future marketing budgets towards customers who generate more return.

### Research question
We want to know if higher marketing spend per customer lead to higher purchase amounts by using 'marketing_spend' and 'purchase_amount' from the campaign data. A linear regression model will be used to determine if marketing spend can effectively predict customer purchase amount.

### Dataset Introduction
```{r}
campaign_data <- read.csv("data/35789190_Pei_Ang.csv")

campaign_data_clean <- campaign_data |> 
    mutate(signup_date = na_if(signup_date, "N/A"),
        signup_date = as_date(parse_date_time(signup_date, orders = c("ymd", "dmy", "BdY")))) |> 
    filter(!is.na(purchase_amount)) |> 
    select(-notes)
```

The cleaned dataset records a total of 132 different customers. It keeps a record of the 'signup_date', 'marketing_spend', number of website 'visits', 'purchase_amount', and the customer 'segment' (Consumer, SMB or Enterprise).

During cleaning, 'signup_date' was stored as a character string with inconsistent formats (e.g. '2025-08-22', 'May 17, 2025', '21/12/2024'). It was then converted to a consistent ISO date format. 

The'notes' column was also removed as it was to inconsistently documented and not relevant to the research question. 

Rows with missing 'purchase_amount' were also removed as they are unrecorded data that cannot contribute to the analysis.

#### Dataset Description
The cleaned data set contains `r nrow(campaign_data_clean)` observations and `r ncol(campaign_data_clean)` variables.


```{r}
ggplot(campaign_data_clean, aes(x = marketing_spend, y = purchase_amount)) + 
    geom_point() +
    labs(title = "Marketing Spend vs Purchase Amount",
        x = "Marketing Spend ($)",
        y = "Purchase Amount ($)")
```